Stellar Bars in Isolated Gas-Rich Spiral Galaxies Do Not Slow Down

### 2023-06-06 paper/ms.tex
Update citation of Aumer and Schonrich

After $5\,\textrm{Gyr}$, the $10\,\Msun/\textrm{pc}^2$ simulation has a gas
fraction of $5.7\%$, but still exhibits constant pattern speed behavior. As a
result, we conclude that for the disk, bar, and halo properties considered in
this work, a gas fraction of only approximately $5\%$ is necessary in order for
the proposed stabilizing mechanism to operate. {\bf We stress that this gas
fraction threshold is only for the system considered in this work. Systems with
different structural parameters may require a different threshold. For example,
\citet{2015MNRAS.454.3166A} find slowdown behavior in a barred disk $10$ times
less massive than ours with a gas fraction of $10\%$. To make things more
complicated, \citet{2010ApJ...719.1470V} find that the gas fraction cutoff
varies with the softening length used. Determining exactly how the gas fraction
cutoff varies with these properties deserves further attention.}

@@

\citet{2015MNRAS.454.3166A} describe a model containing gas and stars which
slows down with time. In their model gas is added to the system to target a gas
fraction of $10\%$. However, their disk is about a factor of $10$ less massive
than the disk considered in this work. The necessary gas fraction for a stable
pattern speed probably depends on galaxy properties like mass. It is unclear
whether $10\%$ is sufficient for their bar to have a stable pattern speed.

>>>>

After $5\,\textrm{Gyr}$, the $10\,\Msun/\textrm{pc}^2$ simulation has a gas
fraction of $5.7\%$, but still exhibits constant pattern speed behavior. As a
result, we conclude that for the disk, bar, and halo properties considered in
this work, a gas fraction of only approximately $5\%$ is necessary in order for
the proposed stabilizing mechanism to operate. {\bf We stress that this gas
fraction threshold is only for the system considered in this work. Systems with
different structural parameters may require a different threshold. For example,
\citet{2015MNRAS.454.3166A} find slowdown behavior in a barred disk initially
$10$ times less massive than ours with a gas fraction of $10\%$. To make things
more complicated, \citet{2010ApJ...719.1470V} find that the gas fraction cutoff
varies with the softening length used. Determining exactly how the gas fraction
cutoff varies with these properties deserves further attention.}

@@

\citet{2015MNRAS.454.3166A} describe a model containing gas and stars which
slows down with time. In their model gas is added to the system to target a gas
fraction of $10\%$. {\bf Their disk is initially a factor of $10$ less massive
than the disk considered in this work, but they grow their disk to be about the
same mass as ours. They find their bar lengthens and slow down with time, which
they attribute to the dark matter halo slowdown dominating over the gas inflow.
However, it may also be the case that a bar in a disk grown in their way
naturally extends its length as fresh material to be captured by the bar is
added to the system. A useful experiment would be to grow a barred disk with a
static dark matter halo to see if its pattern speed evolution mimics theirs, to
determine if their lengthening and slowing down is truly attributed to the halo
friction.}

However, their disk is about a factor of $10$ less massive
than the disk considered in this work. The necessary gas fraction for a stable
pattern speed probably depends on galaxy properties like mass. It is unclear
whether $10\%$ is sufficient for their bar to have a stable pattern speed.
